---
title: "bf_test_caviar"
author: "Matthew Stephens"
date: "2019-06-01"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

## Introduction

This is computation of log-BFs based on code from Caviar (see end for code)

```{r}
library(mvtnorm)
library(data.table)
lbf = function(Zcc,Rcc,NCP){
  p = length(Zcc)
  if(p==1){
    return(dnorm(Zcc,0,Rcc+Rcc*NCP*Rcc,log=TRUE) - dnorm(Zcc,0,Rcc,log=TRUE))
  } else {
    return(mvtnorm::dmvnorm(Zcc, mean=rep(0,p), Rcc + Rcc %*% diag(NCP,p) %*% Rcc, log=TRUE) - mvtnorm::dmvnorm(Zcc, mean = rep(0, p), Rcc, log=TRUE))
  }
}
```

```{r}
data = readRDS('output/SuSiEFD/small_data_68.rds')
r.in = as.matrix(fread('output/SuSiEFD/small_data_68.ld_in_file.in.ld'))
r.out = as.matrix(fread('output/SuSiEFD/small_data_68.ld_out_file.out.ld'))
sim = readRDS('output/SuSiEFD/small_data_68_sim_gaussian_2.rds')
ss = readRDS('output/SuSiEFD/small_data_68_sim_gaussian_2_get_sumstats_1.rds')
z = ss$sumstats$bhat/ss$sumstats$shat
r.out.addz = cov2cor((data$N_out-1) * r.out+tcrossprod(z))
```

The true causal is 267. Susie gets 420 as a false discovery, and another CS containing SNPs correlated with 267.
```{r}
z[c(7,8 ,16 ,29, 35, 36, 37,267,420)]
```

The following shows that, using out of sample LD, indeed the BF for 7 and 420 is much higher than 7 alone (or 267 alone). [from caviar code NCP in caviar is set to be 5.2]
```{r}
lbf_index = function(index,NCP){lbf(z[index],r.out.addz[index,index],NCP)}
lbf_index(7,5.2)
lbf_index(c(7,267),5.2)
lbf_index(c(7,420),5.2)
lbf_index(c(267,420),5.2)
```

And if we just look at the BFs in combination with SNP 7 the posterior
on 420 is very near 1.
```{r}
lbf_with_7 = rep(0,length(z)) 
for(i in 1:length(z)){
  lbf_with_7[i] = lbf_index(c(7,i),5.2)
}
lbf_with_7[7]=lbf_index(7,5.2)
par(mfrow=c(1,2))
plot(lbf_with_7)
plot(exp(lbf_with_7-max(lbf_with_7))/sum(exp(lbf_with_7-max(lbf_with_7))))
```

log-BF from Caviar:

```{r}
lbf.cavair = read.table('test2_ll.log', skip = 10, sep=' ')
```
The lbf for SNP 7 is
```{r}
lbf.cavair[7, 2]
```
The lbf for SNP 7, 267 is
```{r}
lbf.cavair[lbf.cavair[,1]=='6,266,',2]
```
The lbf for SNP 7, 420 is
```{r}
lbf.cavair[lbf.cavair[,1]=='6,419,',2]
```
The lbf for SNP 267, 420 is
```{r}
lbf.cavair[lbf.cavair[,1]=='266,419,',2]
```

```{r}
idx = c(1008, 2008, 3007, 4005, 5002, 5998, 7, 6994:7988)
lbf_7 = lbf.cavair[idx, 2]
par(mfrow=c(1,2))
plot(lbf_7, ylab='lbf caviar with 7')
plot(exp(lbf_7-max(lbf_7))/sum(exp(lbf_7-max(lbf_7))))
```

The correlation matrix in CAVIAR has diagonal 1.36. 

```{r}
r.tmp = r.out.addz
diag(r.tmp) = 1.36
lbf_index = function(index,NCP){lbf(z[index],r.tmp[index,index],NCP)}
lbf_index(7,5.2)
lbf_index(c(7,267),5.2)
lbf_index(c(7,420),5.2)
lbf_index(c(267,420),5.2)
```

```{r}
lbf_with_7 = rep(0,length(z)) 
for(i in 1:length(z)){
  lbf_with_7[i] = lbf_index(c(7,i),5.2)
}
lbf_with_7[7]=lbf_index(7,5.2)
par(mfrow=c(1,2))
plot(lbf_with_7)
plot(exp(lbf_with_7-max(lbf_with_7))/sum(exp(lbf_with_7-max(lbf_with_7))))
```

Fit susie with lambda = 0.36

```{r}
library(susieR)
fit_susie = susie_rss(z, r.out.addz, estimate_residual_variance = FALSE, L=2, lambda=0.36, track_fit = TRUE)
susie_plot(fit_susie, y='PIP', b = sim$meta$true_coef)
```

Using lambda = 0.36, det($R+\lambda I$) > 0. 


# Caviar code
This code is from CAVIAR for reference:
```
// cc=causal SNPs
// Rcc = LD of causal SNPs
// Zcc = Z-score of causal SNPs
// dmvnorm(Zcc, mean=rep(0,nrow(Rcc)), Rcc + Rcc %*% Rcc) / dmvnorm(Zcc, rep(0, nrow(Rcc)), Rcc))
//
double PostCal::fastLikelihood(int * configure, double * stat, double NCP) {
	int causalCount = 0;
	vector <int> causalIndex;
	for(int i = 0; i < snpCount; i++) {
		causalCount += configure[i];
		if(configure[i] == 1)
			causalIndex.push_back(i);
	}
	
	if (causalCount == 0) {
		int maxVal = 0;
		for(int i = 0; i < snpCount; i++) {
			if (maxVal < abs(stat[i]))
				maxVal = stat[i];
		}
	}

	mat Rcc(causalCount, causalCount, fill::zeros);
	mat Zcc(causalCount, 1, fill::zeros);
	mat mean(causalCount, 1, fill::zeros);
	mat diagC(causalCount, causalCount, fill::zeros);

	for (int i = 0; i < causalCount; i++){
		for(int j = 0; j < causalCount; j++) {
			Rcc(i,j) = sigmaMatrix(causalIndex[i], causalIndex[j]);
		}
		Zcc(i,0) = stat[causalIndex[i]];
		diagC(i,i) = NCP;
	}
		
	return fracdmvnorm(Zcc, mean, Rcc, diagC, NCP);
}


// We compute dmvnorm(Zcc, mean=rep(0,nrow(Rcc)), Rcc + Rcc %*% Rcc) / dmvnorm(Zcc, rep(0, nrow(Rcc)), Rcc))
// togheter to avoid numerical over flow
double PostCal::fracdmvnorm(mat Z, mat mean, mat R, mat diagC, double NCP) {
        mat newR = R + R * diagC  * R;
        mat ZcenterMean = Z - mean;
        //mat res1 = trans(ZcenterMean) * inv(R) * (ZcenterMean);
        //mat res2 = trans(ZcenterMean) * inv(newR) *  (ZcenterMean);
	mat res1 = trans(ZcenterMean) * solve(R, eye(size(R))) * (ZcenterMean);
	mat res2 = trans(ZcenterMean) * solve(newR, eye(size(newR))) *  (ZcenterMean);
        double v1 = res1(0,0)/2-res2(0,0)/2;
	//CHANGE: MOVE FORM NORMAL CALCULATION TO LOG SPACE
        //return(exp(v1)/sqrt(det(newR))* sqrt(det(R)));
        return(v1 - log( sqrt(det(newR)) ) + log( sqrt(det(R)) ) );
}
```
