---
title: "Don't Stop Problem "
author: "Yuxin Zou"
date: "3/11/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r message=FALSE}
library(susieR)
library(knitr)
library(kableExtra)
R.utils::sourceDirectory("~/Documents/GitHub/susieR/inst/code/susiez_num/")
```

Data: SuSiE vs DAP: data 31_35 (lower power)

```{r data}
X = readRDS('data/random_data_31.rds')$X
R = cor(X)
data = readRDS('data/random_data_31_sim_gaussian_35.rds')
y = data$Y
beta = data$meta$true_coef
sumstats = readRDS('data/random_data_31_sim_gaussian_35_get_sumstats_1.rds')
zscores = sumstats$sumstats$bhat/sumstats$sumstats$shat
```
We randomly generated 1200 by 1000 matrix X, each entry is random from N(0,1). The variables are independent. There are 5 signals in the simulated data, total PVE is 0.8. The true signals are `r which(beta!=0)`. 
```{r}
plot(zscores, pch=16, main='z scores')
pos = 1:length(zscores)
points(pos[beta!=0],zscores[beta!=0],col=2,pch=16)
susie_plot(zscores, y = "z", b = beta, main='p values from z scores')
```

```{r eval=FALSE}
fit_1 = susie_z_general_num(zscores, R, lambda = 1e-6, track_fit = TRUE, verbose = TRUE, max_iter = 100, estimate_prior_method = 'EM')
```

```{r loadfit1}
fit_1 = readRDS('output/random_data_31_35_fit_em.rds')
```

The algorithm fails to stop. 

The objective is `r susie_get_objective(fit_1)`.

```{r}
susie_plot(fit_1, y='PIP', b=beta)
```

The estimated prior variance at last 10 iterations are
```{r checkfit1V}
Vs = matrix(NA, 11, 10)
for(i in 1:10){
  Vs[i,] = fit_1$trace[[90+i]]$V
}
Vs[11,] = fit_1$V
row.names(Vs) = paste0('Iter: ', 91:101)
Vs %>% kable() %>% kable_styling()
```

Fit model with initial prior variance 50:
```{r}
fit_2 = susie_z_general_num(zscores, R, lambda = 1e-6, track_fit = TRUE, verbose = TRUE, scaled_prior_variance = 50, estimate_prior_method = 'EM')
```

The algorithm stops. The objective is `r susie_get_objective(fit_2)`. 

```{r}
susie_plot(fit_2, y='PIP', b=beta)
```

The estimated prior variances are
```{r}
fit_2$V %>% kable() %>% kable_styling()
```

```{r}
fit_3 = susie_z_general_num(zscores, R, lambda = 1e-6, track_fit = TRUE, verbose = TRUE, s_init = fit_2, scaled_prior_variance = fit_2$V)
susie_plot(fit_3, y='PIP', b=beta)
```

Fit model using 'optim':
```{r}
fit_4 = susie_z_general_num(zscores, R, lambda = 1e-6, track_fit = TRUE, verbose = TRUE, estimate_prior_method = 'optim')
```

The objective is `r susie_get_objective(fit_4)`. 

```{r}
susie_plot(fit_4, y='PIP', b=beta)
```

The estimated prior variances are
```{r}
fit_4$V %>% kable() %>% kable_styling()
```
