---
title: "Investigate"
author: "Yuxin Zou"
date: "3/6/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r message=FALSE}
library(susieR)
library(R.utils)
```

## 1. 
$$
\left(\begin{array} c 2 \\ 2.01 \end{array}\right) \sim N_2(\mathbf{1}\mathbf{1}^{T} \mathbf{0}, \sigma^2 \mathbf{1}\mathbf{1}^{T} + \lambda I)
$$

```{r}
z = c(2, 2.01)
R = matrix(1, 2,2)
```

Model with var $\sigma^2(R + \lambda I)$.
```{r fit1}
sourceDirectory("~/Documents/GitHub/susieR/inst/code/susiez_fix/")
fit_1 = susie_z_general_fix(z, R, lambda = 0.1, restrict = FALSE, estimate_prior_method = 'EM')
```
The estimated residual variance is
```{r}
fit_1$sigma2
```

Model with var $\sigma^2R + \lambda I$.
```{r fit2}
sourceDirectory("~/Documents/GitHub/susieR/inst/code/susiez_num/")
fit_2 = susie_z_general_num(z, R, lambda = 0.1, restrict = FALSE, estimate_prior_method = 'EM')
```
The estimated residual variance is
```{r}
fit_2$sigma2
```

The model with var $\sigma^2R + \lambda I$ gives the estimated residual variance close to 4.

We use the model with var $\sigma^2R + \lambda I$ in the following investigation.

## 2. 
$$
\left(\begin{array} c 1 \\ 1.01 \end{array}\right) \sim N_2(\mathbf{1}\mathbf{1}^{T} \mathbf{0}, \sigma^2 \mathbf{1}\mathbf{1}^{T} + \lambda I)
$$

```{r}
z = c(1, 1.01)
R = matrix(1, 2, 2)
```

Model with var $\sigma^2R + \lambda I$. $\lambda=0.1$
```{r}
fit_3 = susie_z_general_num(z, R, verbose=TRUE, lambda = 0.1, restrict = TRUE, estimate_prior_method = 'EM')
susie_plot(fit_3, y = 'PIP')
```

There are no significant signal.

$\lambda=0$
```{r}
fit_4 = susie_z_general_num(z, R, verbose=TRUE, lambda = 0, restrict = TRUE, estimate_prior_method = 'EM')
susie_plot(fit_4, y = 'PIP')
```

```{r}
z = c(6, 6.01)
R = matrix(1, 2, 2)
```

Model with var $\sigma^2R + \lambda I$. $\lambda=0.1$
```{r}
fit_5 = susie_z_general_num(z, R, verbose=TRUE, lambda = 0.1, restrict = TRUE, estimate_prior_method = 'EM')
susie_plot(fit_5, y = 'PIP')
```

We find the significant signal.

$\lambda=0$
```{r}
fit_6 = susie_z_general_num(z, R, verbose=TRUE, lambda = 0, restrict = TRUE, estimate_prior_method = 'EM')
susie_plot(fit_6, y = 'PIP')
```

