---
title: "Probelm set investigate"
author: "Yuxin Zou"
date: 2019-2-14
output: 
  workflowr::wflow_html:
    code_folding: hide
---

The simulated data has 1 true effects. The PVE is 0.5.

```{r}
library(kableExtra)
library(knitr)
library(susieR)
library(png)
data = readRDS('data/sim_gaussian_75.rds')
n = data$n
beta = numeric(data$p)
beta[data$beta_idx] = data$beta_val
z = data$ss$effect/data$ss$se
susie_plot(z, y = "z", b=beta)
```

The true signals are at `r which(beta!=0)`.

```{r eval=FALSE, echo=FALSE}
library(dscrutils)
dscout = dscquery('output/susie_z_Problem75', target = 'score_susie score_dap score_finemap score_susie.total score_susie.valid score_susie.size score_susie.purity score_susie.top score_susie.objective score_susie.converged score_susie.overlap score_susie.signal_pip score_dap.total score_dap.valid score_dap.size score_dap.avgr2 score_dap.top score_dap.overlap score_dap.signal_pip score_finemap.total score_finemap.valid score_finemap.size score_finemap.signal_pip')
```

```{r}
dscout = readRDS('output/dscoutProblem75.rds')
fit_susie = readRDS('~/Documents/GitHub/dsc-finemap/output/susie_z_Problem75/susie_z/full_data_1_get_sumstats_1_susie_z_1.rds')
```

Using `SuSiE z`, it captures the causal SNPs. The PIP plot is
```{r susie_z, echo=FALSE, fig.cap="SuSiE z PIP", out.width = '100%'}
susie_plot(fit_susie$fitted[[1]], y = 'PIP', b = beta)
```

The model from DAP-G finds 8 credible sets, 1 of them contain true signals. 

![DAP result: A is the probability of different credible set. B is the PIP of the top 10 SNPs](P75full_data_1_get_sumstats_1_dap_z_1_plot_dap_1.plot_file.pdf){width=100%;height=7cm}

The 95% confidence set from finemap contains 1000 SNPs, 1 of them are true signals. It prefers the model with 3 causal SNPs. Both finemap and dap have many false positives. 

![finemap result: A is the posterior of number of causals. B is the probability of different configuration. C is the PIP of the top 10 SNPs.](P75full_data_1_get_sumstats_1_finemap_1_plot_finemap_1.plot_file.pdf){width=15cm;height=7cm}

```{r fig.align='center', fig.cap=c("finemap result: A is the posterior of number of causals. B is the probability of different configuration. C is the PIP of the top 10 SNPs."), echo=FALSE, out.width = '100%'}
imgfinemap <- readPNG('output/P75full_data_1_get_sumstats_1_finemap_1_plot_finemap_1.plot_file.png')
grid::grid.raster(imgfinemap)
```

Comparing the PIP for the true signal:
```{r}
susie_pip = matrix(as.numeric(dscout[1, 11]), 1,1)
dap_pip = matrix(as.numeric(dscout[3, 19]), 1,1)
finemap_pip = matrix(as.numeric(dscout[4, 24]), 1,1)
tmp = rbind(susie_pip, dap_pip, finemap_pip)
row.names(tmp) = c('susie z', 'dap', 'finemap')
colnames(tmp) = paste0('Signal ', 1)
tmp %>% kable() %>% kable_styling()
```


















