---
title: "SuSiE FD Example"
author: "Yuxin Zou"
date: "5/14/2019"
output:   
  workflowr::wflow_html:
    code_folding: hide
    self_contained: false
---

```{r message=F, warning=F}
library(data.table)
library(susieR)
```

The data is simulated with PVE 0.2, n signal = 1.

Read data:

```{r}
data = readRDS('output/SuSiEFD/small_data_68.rds')
r.in = as.matrix(fread('output/SuSiEFD/small_data_68.ld_in_file.in.ld'))
r.out = as.matrix(fread('output/SuSiEFD/small_data_68.ld_out_file.out.ld'))
sim = readRDS('output/SuSiEFD/small_data_68_sim_gaussian_2.rds')
ss = readRDS('output/SuSiEFD/small_data_68_sim_gaussian_2_get_sumstats_1.rds')
```

Plot p values
```{r}
z = ss$sumstats$bhat/ss$sumstats$shat
r.out.addz = cov2cor((data$N_out-1) * r.out+tcrossprod(z))
susie_plot(z, y='z', b = sim$meta$true_coef)
```

The true signal is 267.

The models below are fitted without estimating residual variance.

## SuSiE rss

### Using in sample R
```{r}
fit_susierss_in = susie_rss(z, R = r.in, estimate_residual_variance = FALSE, L=2, lambda = 0.1, track_fit = T)
susie_plot(fit_susierss_in, y='PIP', b = sim$meta$true_coef)
```

### Using out sample R
```{r}
fit_susierss_out = susie_rss(z, R = r.out, estimate_residual_variance = FALSE, L=2, lambda=0.1, track_fit = T)
susie_plot(fit_susierss_out, y='PIP', b = sim$meta$true_coef)
```

### Using out sample R addz

L = 2
```{r}
fit_susierss_out_addz = susie_rss(z, R = r.out.addz, estimate_residual_variance = FALSE, L=2, lambda=0.1, track_fit = TRUE)
susie_plot(fit_susierss_out_addz, y='PIP', b = sim$meta$true_coef)
```

**420 has pip 1.**

Plot each iteration:
```{r}
library(magick)
iters = image_read('output/SuSiEFD/susierss.out.addz.2.gif')
iters
```
The true signal disappears after 3 iterations.

L = 1
```{r}
fit_susierss_out_addz.1 = susie_rss(z, R = r.out.addz, estimate_residual_variance = FALSE, L=1, lambda=0.1, track_fit = TRUE)
susie_plot(fit_susierss_out_addz.1, y='PIP', b = sim$meta$true_coef)
```

The model with L = 2 fails to capture the true signal but it has higher objective value than the model with L=1.

Try with prior variance = 20 and not estimate prior variance:
```{r}
fit_susierss_out_addz.prior = susie_rss(z, R = r.out.addz, estimate_residual_variance = FALSE, L=2, lambda=0.1, track_fit = TRUE, prior_variance = 20, estimate_prior_variance = FALSE)
susie_plot(fit_susierss_out_addz.prior, y='PIP', b = sim$meta$true_coef)
```

## correlation between true signal (267) and false signal (420)

The in sample correlation is
```{r}
r.in[c(267, 420), c(267, 420)]
```

The out sample correlation is
```{r}
r.out[c(267, 420), c(267, 420)]
```

The out sample correlation add z is
```{r}
r.out.addz[c(267, 420), c(267, 420)]
```


```{r echo=FALSE, eval=FALSE}
library(RColorBrewer)
library(gplots)
color <- colorRampPalette(c("blue", "white", "red"))(n = 299)

true_coef = which(sim$meta$true_coef != 0)

true_coef_col = rep('white', length(sim$meta$true_coef))
true_coef_col[true_coef] = 'red'
true_coef_col[420] = 'red'
true_coef_col[c(1,100,200,300,400,500,600,700,800,900,1000)] = 'black'
colnames(r.in)[c(1,100,200,300,400,500,600,700,800,900,1000)] = c(1,100,200,300,400,500,600,700,800,900,1000)
colnames(r.in)[-c(1,100,200,300,400,500,600,700,800,900,1000)] = rep(NA, length(colnames(r.in))-11)
colnames(r.in)[true_coef] = true_coef
colnames(r.in)[420] = 420
row.names(r.in) = colnames(r.in)
pdf('../output/SuSiEFD/r.in.pdf')
heatmap.2(r.in[250:430, 250:430], Colv = FALSE, Rowv = FALSE, dendrogram = 'none', symm = TRUE, main = 'R in sample', col=color, colCol=true_coef_col[250:430],colRow = true_coef_col[250:430], density.info = 'none', trace="none", cexRow = 0.8, cexCol = 0.8)
dev.off() 

colnames(r.out)[c(1,100,200,300,400,500,600,700,800,900,1000)] = c(1,100,200,300,400,500,600,700,800,900,1000)
colnames(r.out)[-c(1,100,200,300,400,500,600,700,800,900,1000)] = rep(NA, length(colnames(r.out))-11)
colnames(r.out)[true_coef] = true_coef
colnames(r.out)[420] = 420
row.names(r.out) = colnames(r.out)
pdf('../output/SuSiEFD/r.out.pdf')
heatmap.2(r.out[250:430, 250:430], Colv = FALSE, Rowv = FALSE, dendrogram = 'none', symm = TRUE, main = 'R out sample', col=color, colCol=true_coef_col[250:430],colRow = true_coef_col[250:430], density.info = 'none', trace="none", cexRow = 0.8, cexCol = 0.8)
dev.off() 

colnames(r.out.addz)[c(1,100,200,300,400,500,600,700,800,900,1000)] = c(1,100,200,300,400,500,600,700,800,900,1000)
colnames(r.out.addz)[-c(1,100,200,300,400,500,600,700,800,900,1000)] = rep(NA, length(colnames(r.out.addz))-11)
colnames(r.out.addz)[true_coef] = true_coef
colnames(r.out.addz)[420] = 420
row.names(r.out.addz) = colnames(r.out)
pdf('../output/SuSiEFD/r.out.addz.pdf')
heatmap.2(r.out.addz[250:430, 250:430], Colv = FALSE, Rowv = FALSE, dendrogram = 'none', symm = TRUE, main = 'R out sample add z', col=color, colCol=true_coef_col[250:430],colRow = true_coef_col[250:430], density.info = 'none', trace="none", cexRow = 0.8, cexCol = 0.8)
dev.off() 
```
