---
title: "Compare in-sample R vs out-sample R (equal effect)"
author: "Yuxin Zou"
date: "4/14/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

The design matrix X are real human genotype data from GTEx project, the 150 data in `dsc-finemap` repo. We simulate under various number of causal variables (1,3,5) and total percentage of variance explained (0.05, 0.2, 0.6, 0.8). We set effect size of each causal variable to be **equal**. Using the summary statistics from univariate regression, we fit SuSiE model using in-sample/out-sample correlation matrix, and compare their results.


```{r}
library(dscrutils)
library(tibble)
library(kableExtra)
```

## Import DSC results

```{r eval=FALSE}
dscout = dscquery('r_compare_data_signal', targets = 'get_sumstats sim_gaussian.pve sim_gaussian.n_signal sim_gaussian.effect_weight data.N_in susie_bhat.ld_method susie_z.ld_method finemap.ld_method score_susie.total score_susie.valid score_susie.size score_susie.purity score_susie.top score_susie.converged score_finemap.pip', omit.filenames = FALSE)
dscout.tibble = as_tibble(dscout)
```

```{r}
dscout = readRDS('output/r_compare_dscout_susie_finemappip_tibble.rds')
dscout$method = rep('susie_b', nrow(dscout))
dscout$method[!is.na(dscout$susie_z.ld_method)] = 'susie_rss'
dscout$method[!is.na(dscout$finemap.ld_method)] = 'finemap'

dscout$ld_method = dscout$susie_bhat.ld_method
dscout$ld_method[!is.na(dscout$susie_z.ld_method)] = dscout$susie_z.ld_method[!is.na(dscout$susie_z.ld_method)]
dscout$ld_method[!is.na(dscout$finemap.ld_method)] = dscout$finemap.ld_method[!is.na(dscout$finemap.ld_method)]
dscout$sim_gaussian.effect_weight[which(dscout$sim_gaussian.effect_weight == 'rep(1/n_signal, n_signal)')] = 'equal'
dscout$sim_gaussian.effect_weight[which(dscout$sim_gaussian.effect_weight != 'equal')] = 'notequal'
dscout = dscout[,-c(6,8,9,10)]
colnames(dscout) = c('DSC', 'filename','pve', 'n_signal', 'effect_weight', 'N_in', 'total', 'valid', 'size', 'purity', 'top', 'converged', 'pip', 'method', 'ld_method')
```

```{r}
dscout.equal = dscout[dscout$effect_weight == 'equal',]
dscout.equal.susierss = dscout.equal[dscout.equal$method == 'susie_rss',]
dscout.equal.susieb = dscout.equal[dscout.equal$method == 'susie_b',]
dscout.equal.finemap = dscout.equal[dscout.equal$method == 'finemap',]
```

## susie_bhat

```{r}
dscout.equal.susieb.in_sample = dscout.equal.susieb[dscout.equal.susieb$ld_method == 'in_sample',]
dscout.equal.susieb.out_sample = dscout.equal.susieb[dscout.equal.susieb$ld_method == 'out_sample',]
```

* Converge

The model from susie_bhat all converge. But lots of cases with out-sample R failed (274 out of 1800). The estimated residual variance becomes negative.
```{r}
converge.summary = aggregate(converged ~ ld_method, dscout.equal.susieb, sum)
converge.summary$Fail = 1800 - converge.summary$converged
Fail = converge.summary[converge.summary$Fail!=0,]
Fail[,-2] %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Purity of CS:

```{r}
purity.susieb.in_sample = round(aggregate(purity~n_signal+pve, dscout.equal.susieb.in_sample, mean), 3)
colnames(purity.susieb.in_sample)[colnames(purity.susieb.in_sample) == 'purity'] <- 'purity.in_sample'
purity.susieb.out_sample = round(aggregate(purity~n_signal+pve, dscout.equal.susieb.out_sample[!is.na(dscout.equal.susieb.out_sample$converged),], mean), 3)
colnames(purity.susieb.out_sample)[colnames(purity.susieb.out_sample) == 'purity'] <- 'purity.out_sample'
purity.susieb = merge(purity.susieb.in_sample, purity.susieb.out_sample)

purity.susieb %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Power:

```{r}
valid.in = aggregate(valid ~ n_signal + pve, dscout.equal.susieb.in_sample, sum)
total.in = aggregate(DSC~ n_signal + pve, dscout.equal.susieb.in_sample, length)
total.in$total_true = total.in$DSC * total.in$n_signal
power.susie.in = merge(valid.in, total.in)
power.susie.in$power.susie.in_sample = round(power.susie.in$valid/(power.susie.in$total_true), 3)
colnames(power.susie.in)[colnames(power.susie.in) == 'valid'] <- 'valid.in_sample'
power.susie.in = power.susie.in[,-c(3,4,5)]

valid.out = aggregate(valid ~ n_signal + pve, dscout.equal.susieb.out_sample[!is.na(dscout.equal.susieb.out_sample$converged),], sum)
total.out = aggregate(DSC~ n_signal + pve, dscout.equal.susieb.out_sample[!is.na(dscout.equal.susieb.out_sample$converged),], length)
total.out$total_true = total.out$DSC * total.out$n_signal
power.susie.out = merge(valid.out, total.out)
power.susie.out$power.susie.out_sample = round(power.susie.out$valid/(power.susie.out$total_true), 3)
colnames(power.susie.out)[colnames(power.susie.out) == 'valid'] <- 'valid.out_sample'
power.susie.out = power.susie.out[,-c(3,4,5)]

power.susie = Reduce(function(...) merge(...),
       list(power.susie.in, power.susie.out))
colnames(power.susie) = c('n_signal', 'pve', 'IN sample', 'OUT sample')
power.susie %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F)
```

* FDR
```{r}
valid.in = aggregate(valid ~ n_signal + pve, dscout.equal.susieb.in_sample, sum)
total.in = aggregate(total~ n_signal + pve, dscout.equal.susieb.in_sample, sum)
fdr.in = merge(valid.in, total.in)
fdr.in$fdr.in = round((fdr.in$total - fdr.in$valid)/fdr.in$total, 4)
colnames(fdr.in)[colnames(fdr.in) == 'valid'] <- 'valid.in_sample'
fdr.in = fdr.in[,-c(3,4)]

valid.out = aggregate(valid ~ n_signal + pve, dscout.equal.susieb.out_sample[!is.na(dscout.equal.susieb.out_sample$converged),], sum)
total.out = aggregate(total~ n_signal + pve, dscout.equal.susieb.out_sample[!is.na(dscout.equal.susieb.out_sample$converged),], sum)
fdr.out = merge(valid.out, total.out)
fdr.out$fdr.out = round((fdr.out$total - fdr.out$valid)/fdr.out$total, 4)
colnames(fdr.out)[colnames(fdr.out) == 'valid'] <- 'valid.out_sample'
fdr.out = fdr.out[,-c(3,4)]

fdr = Reduce(function(...) merge(...),
       list(fdr.in, fdr.out))
colnames(fdr) = c('n_signal', 'pve', 'IN sample', 'OUT sample')
fdr %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F)
```

## susie_rss

```{r}
dscout.equal.susierss.in_sample = dscout.equal.susierss[dscout.equal.susierss$ld_method == 'in_sample',]
dscout.equal.susierss.out_sample = dscout.equal.susierss[dscout.equal.susierss$ld_method == 'out_sample',]
```

* Converge

There are cases fail to converge in susie_rss.
```{r}
converge.summary = aggregate(converged ~ pve + n_signal+ld_method, dscout.equal.susierss, sum)
converge.summary$NotConverge = 150 - converge.summary$converged
NotConverge = converge.summary[converge.summary$NotConverge!=0,]
colnames(NotConverge) = c('pve', 'n_signal', 'ld', 'converged', 'NotConverge(out of 150)')
NotConverge[,-4] %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Purity of CS:

```{r}
purity.susierss.in_sample = round(aggregate(purity~n_signal+pve, dscout.equal.susierss.in_sample[dscout.equal.susierss.in_sample$converged==1,], mean), 3)
colnames(purity.susierss.in_sample)[colnames(purity.susierss.in_sample) == 'purity'] <- 'purity.in_sample'
purity.susierss.out_sample = round(aggregate(purity~n_signal+pve, dscout.equal.susierss.out_sample[dscout.equal.susierss.out_sample$converged==1,], mean), 3)
colnames(purity.susierss.out_sample)[colnames(purity.susierss.out_sample) == 'purity'] <- 'purity.out_sample'
purity.susierss = merge(purity.susierss.in_sample, purity.susierss.out_sample)

purity.susierss %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Power:

```{r}
valid.in = aggregate(valid ~ n_signal + pve, dscout.equal.susierss.in_sample[dscout.equal.susierss.in_sample$converged==1,], sum)
total.in = aggregate(DSC~ n_signal + pve, dscout.equal.susierss.in_sample[dscout.equal.susierss.in_sample$converged==1,], length)
total.in$total_true = total.in$DSC * total.in$n_signal
power.susie.in = merge(valid.in, total.in)
power.susie.in$power.susie.in_sample = round(power.susie.in$valid/(power.susie.in$total_true), 3)
colnames(power.susie.in)[colnames(power.susie.in) == 'valid'] <- 'valid.in_sample'
power.susie.in = power.susie.in[,-c(3,4,5)]

valid.out = aggregate(valid ~ n_signal + pve, dscout.equal.susierss.out_sample[dscout.equal.susierss.out_sample$converged ==1,], sum)
total.out = aggregate(DSC~ n_signal + pve, dscout.equal.susierss.out_sample[dscout.equal.susierss.out_sample$converged ==1,], length)
total.out$total_true = total.out$DSC * total.out$n_signal
power.susie.out = merge(valid.out, total.out)
power.susie.out$power.susie.out_sample = round(power.susie.out$valid/(power.susie.out$total_true), 3)
colnames(power.susie.out)[colnames(power.susie.out) == 'valid'] <- 'valid.out_sample'
power.susie.out = power.susie.out[,-c(3,4,5)]

power.susie = Reduce(function(...) merge(...),
       list(power.susie.in, power.susie.out))
colnames(power.susie) = c('n_signal', 'pve', 'IN sample', 'OUT sample')
power.susie %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F)
```

* FDR:

```{r}
valid.in = aggregate(valid ~ n_signal + pve, dscout.equal.susierss.in_sample[dscout.equal.susierss.in_sample$converged==1,], sum)
total.in = aggregate(total~ n_signal + pve, dscout.equal.susierss.in_sample[dscout.equal.susierss.in_sample$converged==1,], sum)
fdr.in = merge(valid.in, total.in)
fdr.in$fdr.in = round((fdr.in$total - fdr.in$valid)/fdr.in$total, 4)
colnames(fdr.in)[colnames(fdr.in) == 'valid'] <- 'valid.in_sample'
fdr.in = fdr.in[,-c(3,4)]

valid.out = aggregate(valid ~ n_signal + pve, dscout.equal.susierss.out_sample[dscout.equal.susierss.out_sample$converged==1,], sum)
total.out = aggregate(total~ n_signal + pve, dscout.equal.susierss.out_sample[dscout.equal.susierss.out_sample$converged==1,], sum)
fdr.out = merge(valid.out, total.out)
fdr.out$fdr.out = round((fdr.out$total - fdr.out$valid)/fdr.out$total, 4)
colnames(fdr.out)[colnames(fdr.out) == 'valid'] <- 'valid.out_sample'
fdr.out = fdr.out[,-c(3,4)]

fdr = Reduce(function(...) merge(...),
       list(fdr.in, fdr.out))
colnames(fdr) = c('n_signal', 'pve', 'IN sample', 'OUT sample')
fdr %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F)
```

