---
title: "Power vs FDR Plot"
author: "Yuxin Zou"
date: "6/17/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

```{r message=F, warning=F}
library(ggplot2)
library(cowplot)
library(gridExtra)
library(dplyr)
```

```{r}
caviar = readRDS('output/r_compare_mafall_caviar_ROC.rds')
finemap.l2 = readRDS('output/r_compare_mafall_FINEMAP_L2_ROC.rds')
finemap.l5 = readRDS('output/r_compare_mafall_FINEMAP_L5_ROC.rds')
susieb.l2 = readRDS('output/r_compare_maf0_SuSiEb_L2_ROC.rds')
susieb.maf.l2 = readRDS('output/r_compare_maf0.05_SuSiEb_L2_ROC.rds')
susieb.l5 = readRDS('output/r_compare_maf0_SuSiEb_L5_ROC.rds')
susieb.maf.l5 = readRDS('output/r_compare_maf0.05_SuSiEb_L5_ROC.rds')
susierss.l2 = readRDS('output/r_compare_maf0_SuSiERSS_L2_ROC.rds')
susierss.maf.l2 = readRDS('output/r_compare_maf0.05_SuSiERSS_L2_ROC.rds')
susierss.l5 = readRDS('output/r_compare_maf0_SuSiERSS_L5_ROC.rds')
susierss.maf.l5 = readRDS('output/r_compare_maf0.05_SuSiERSS_L5_ROC.rds')
```

The design matrix X are real human genotype data from GTEx project, the 150 data in `dsc-finemap` repo. We randomly separate individuals into two groups, in sample and out sample group, and compute the corresponding correlation matrix. After filtering for MAF (0% or 5%), we simulate data under various number of causal variables (1,2) and total percentage of variance explained (0.1, 0.2). We set effect size of each causal variable to be **equal**. Using the summary statistics from univariate regression with in sample individuals, we fit SuSiE model using in-sample/out-sample correlation matrix, and compare their results.

We compare results from CAVIAR(v2.0), FINEMAP(v1.1), SuSiE bhat and SuSiE RSS. The results from MAF filtered data are plotted using dark color. 

We didn't include FINEMAP(v1.3.1), because it has error in data with MAF threshold 5%.

Summary:

1. Using MAF filter, CAVIAR, SuSiE bhat and SuSiE RSS perform similarly using out sample correlation matrix adding z. They all **outperform** FINEMAP.

2. Applying MAF filter **decreases** the FDR.

## L=2

We check the results using 2 max causals in all methods.

### NOT estimate residual variance

#### Power vs FDR

```{r message=F, warning=F}
chunks = 0
smooth = FALSE
colors = c('lavenderblush', 'red', 'lightcyan', 'blue', 'darkseagreen1', 'green', 'lightgoldenrod1', 'goldenrod2')

library(scam)
create_chunks = function(item, n) {
  splitted = suppressWarnings(split(item, 1:n))
  return(c(splitted[[1]], splitted[[length(splitted)]][length(splitted[[length(splitted)]])]))
}
make_smooth = function(x,y,subset=chunks, smooth = FALSE){
  if (smooth) {
    if (subset < length(x) && subset > 0) {
      x = create_chunks(x, subset)
      y = create_chunks(y, subset)
    }
    dat = data.frame(cbind(x,y))
    colnames(dat) = c('x','y')
    y=predict(scam(y ~ s(x, bs = "mpi"), data = dat))
    }
  return(list(x=x,y=y))
}
add_text = function(thresholds,x,y,threshold,color,delta = -0.06) {
  idx = which(thresholds == threshold)
  text(x[idx] - delta,y[idx],labels = threshold,col = color,cex = 0.8)
  points(x[idx], y[idx], col = color)
}
```

##### IN sample
```{r}
roc.notest = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l2$in_sample, FINEMAP.MAF = finemap.l2$maf.in_sample, SuSiEb = susieb.l2$in_sample.notest, SuSiEb.MAF = susieb.maf.l2$maf.in_sample.notest, SuSiErss = susierss.l2$in_sample.notest, SuSiErss.MAF = susierss.maf.l2$maf.in_sample.notest)
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
library(graphics)
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l2$out_sample, FINEMAP.MAF = finemap.l2$maf.out_sample, SuSiEb = susieb.l2$out_sample.notest, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.notest, SuSiErss = susierss.l2$out_sample.notest, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.notest)
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.4), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.4), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.02)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))

labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l2$out_sample.addz, FINEMAP.MAF = finemap.l2$maf.out_sample.addz, SuSiEb = susieb.l2$out_sample.addz.notest, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.addz.notest, SuSiErss = susierss.l2$out_sample.addz.notest, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.addz.notest)
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT addz Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
# legend("topright", inset=c(1,0), legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))
```

#### ROC

##### IN sample
```{r}
roc.notest = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l2$in_sample, FINEMAP.MAF = finemap.l2$maf.in_sample, SuSiEb = susieb.l2$in_sample.notest, SuSiEb.MAF = susieb.maf.l2$maf.in_sample.notest, SuSiErss = susierss.l2$in_sample.notest, SuSiErss.MAF = susierss.maf.l2$maf.in_sample.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta = -0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l2$out_sample, FINEMAP.MAF = finemap.l2$maf.out_sample, SuSiEb = susieb.l2$out_sample.notest, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.notest, SuSiErss = susierss.l2$out_sample.notest, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp

for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))

labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l2$out_sample.addz, FINEMAP.MAF = finemap.l2$maf.out_sample.addz, SuSiEb = susieb.l2$out_sample.addz.notest, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.addz.notest, SuSiErss = susierss.l2$out_sample.addz.notest, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.addz.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp

for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT addz ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
# legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd=rep(3, i))
```

### Estimate residual variance

#### Power vs FDR

##### IN sample
```{r}
roc.est = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l2$in_sample, FINEMAP.MAF = finemap.l2$maf.in_sample, SuSiEb = susieb.l2$in_sample.est, SuSiEb.MAF = susieb.maf.l2$maf.in_sample.est, SuSiErss = susierss.l2$in_sample.est, SuSiErss.MAF = susierss.maf.l2$maf.in_sample.est)
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l2$out_sample, FINEMAP.MAF = finemap.l2$maf.out_sample, SuSiEb = susieb.l2$out_sample.est, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.est, SuSiErss = susierss.l2$out_sample.est, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.est)
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))

labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l2$out_sample.addz, FINEMAP.MAF = finemap.l2$maf.out_sample.addz, SuSiEb = susieb.l2$out_sample.addz.est, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.addz.est, SuSiErss = susierss.l2$out_sample.addz.est, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.addz.est)
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT addz Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.02)
  labels[i] = method
  i = i + 1
}
# legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd = rep(3, i))
```

#### ROC

##### IN sample
```{r}
roc.est = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l2$in_sample, FINEMAP.MAF = finemap.l2$maf.in_sample, SuSiEb = susieb.l2$in_sample.est, SuSiEb.MAF = susieb.maf.l2$maf.in_sample.est, SuSiErss = susierss.l2$in_sample.est, SuSiErss.MAF = susierss.maf.l2$maf.in_sample.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.005), ylim = c(0,0.6))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l2$out_sample, FINEMAP.MAF = finemap.l2$maf.out_sample, SuSiEb = susieb.l2$out_sample.est, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.est, SuSiErss = susierss.l2$out_sample.est, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp

for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))

labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l2$out_sample.addz, FINEMAP.MAF = finemap.l2$maf.out_sample.addz, SuSiEb = susieb.l2$out_sample.addz.est, SuSiEb.MAF = susieb.maf.l2$maf.out_sample.addz.est, SuSiErss = susierss.l2$out_sample.addz.est, SuSiErss.MAF = susierss.maf.l2$maf.out_sample.addz.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp

for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT addz ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta = -0.0001)
  labels[i] = method
  i = i + 1
}
# legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd=rep(3, i))
```

## L=5

We fit model using 5 max causals in susie bhat, susie rss and finemap. CAVIAR is fitted using 2 max causal.

### NOT estimate residual variance

#### Power vs FDR

##### IN sample
```{r}
roc.notest = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l5$in_sample, FINEMAP.MAF = finemap.l5$maf.in_sample, SuSiEb = susieb.l5$in_sample.notest, SuSiEb.MAF = susieb.maf.l5$maf.in_sample.notest, SuSiErss = susierss.l5$in_sample.notest, SuSiErss.MAF = susierss.maf.l5$maf.in_sample.notest)
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l5$out_sample, FINEMAP.MAF = finemap.l5$maf.out_sample, SuSiEb = susieb.l5$out_sample.notest, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.notest, SuSiErss = susierss.l5$out_sample.notest, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.notest)
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.8), ylim = c(0,0.8))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.8), ylim = c(0,0.8))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.02)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))

labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l5$out_sample.addz, FINEMAP.MAF = finemap.l5$maf.out_sample.addz, SuSiEb = susieb.l5$out_sample.addz.notest, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.addz.notest, SuSiErss = susierss.l5$out_sample.addz.notest, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.addz.notest)
for (method in names(roc.notest)) {
  yy = make_smooth(1 - roc.notest[[method]]$rates$Precision, roc.notest[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT addz Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.4), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
# legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd = rep(3, i))
```

#### ROC

##### IN sample
```{r}
roc.notest = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l5$in_sample, FINEMAP.MAF = finemap.l5$maf.in_sample, SuSiEb = susieb.l5$in_sample.notest, SuSiEb.MAF = susieb.maf.l5$maf.in_sample.notest, SuSiErss = susierss.l5$in_sample.notest, SuSiErss.MAF = susierss.maf.l5$maf.in_sample.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta = -0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l5$out_sample, FINEMAP.MAF = finemap.l5$maf.out_sample, SuSiEb = susieb.l5$out_sample.notest, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.notest, SuSiErss = susierss.l5$out_sample.notest, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp

for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))

labels = vector()
i = 1
roc.notest = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l5$out_sample.addz, FINEMAP.MAF = finemap.l5$maf.out_sample.addz, SuSiEb = susieb.l5$out_sample.addz.notest, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.addz.notest, SuSiErss = susierss.l5$out_sample.addz.notest, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.addz.notest)
tmp = list()
for (method in names(roc.notest)) {
  TPR = roc.notest[[method]]$counts$true_positive/roc.notest[[method]]$counts$total_signal
  FPR = roc.notest[[method]]$counts$false_positive/roc.notest[[method]]$counts$total_null
  threshold = roc.notest[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.notest = tmp

for (method in names(roc.notest)) {
  yy = make_smooth(roc.notest[[method]]$FPR, roc.notest[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT addz ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.notest[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
# legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd=rep(3, i))
```

### Estimate residual variance

#### Power vs FDR

##### IN sample
```{r}
roc.est = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l5$in_sample, FINEMAP.MAF = finemap.l5$maf.in_sample, SuSiEb = susieb.l5$in_sample.est, SuSiEb.MAF = susieb.maf.l5$maf.in_sample.est, SuSiErss = susierss.l5$in_sample.est, SuSiErss.MAF = susierss.maf.l5$maf.in_sample.est)
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.3), ylim = c(0,0.3))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))
```

##### OUT sample

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l5$out_sample, FINEMAP.MAF = finemap.l5$maf.out_sample, SuSiEb = susieb.l5$out_sample.est, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.est, SuSiErss = susierss.l5$out_sample.est, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.est)
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.8), ylim = c(0,0.6))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.8), ylim = c(0,0.6))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.01)
  labels[i] = method
  i = i + 1
}
legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd = rep(3, i))

labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l5$out_sample.addz, FINEMAP.MAF = finemap.l5$maf.out_sample.addz, SuSiEb = susieb.l5$out_sample.addz.est, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.addz.est, SuSiErss = susierss.l5$out_sample.addz.est, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.addz.est)
for (method in names(roc.est)) {
  yy = make_smooth(1 - roc.est[[method]]$rates$Precision, roc.est[[method]]$rates$Recall)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "power", xlab ="FDR", main = 'OUT addz Power vs FDR', bty='l', lwd = 3, xlim = c(0,0.6), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 3, xlim = c(0,0.6), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$rates$Threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.02)
  labels[i] = method
  i = i + 1
}
# legend("topleft", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd = rep(3, i))
```

#### ROC

##### IN sample
```{r}
roc.est = list(CAVIAR = caviar$in_sample, CAVIAR.MAF = caviar$maf.in_sample, FINEMAP = finemap.l5$in_sample, FINEMAP.MAF = finemap.l5$maf.in_sample, SuSiEb = susieb.l5$in_sample.est, SuSiEb.MAF = susieb.maf.l5$maf.in_sample.est, SuSiErss = susierss.l5$in_sample.est, SuSiErss.MAF = susierss.maf.l5$maf.in_sample.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp
```

```{r fig.width=6, fig.height=5}
labels = vector()
i = 1
for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.005), ylim = c(0,0.6))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))
```

##### OUT sample and OUT sample addz

```{r fig.width=12, fig.height=5, fig.align='center'}
par(mfrow=c(1,2))
labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample, CAVIAR.MAF = caviar$maf.out_sample, FINEMAP = finemap.l5$out_sample, FINEMAP.MAF = finemap.l5$maf.out_sample, SuSiEb = susieb.l5$out_sample.est, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.est, SuSiErss = susierss.l5$out_sample.est, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp

for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta=-0.0001)
  labels[i] = method
  i = i + 1
}
legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.7, lwd=rep(3, i))

labels = vector()
i = 1
roc.est = list(CAVIAR = caviar$out_sample.addz, CAVIAR.MAF = caviar$maf.out_sample.addz, FINEMAP = finemap.l5$out_sample.addz, FINEMAP.MAF = finemap.l5$maf.out_sample.addz, SuSiEb = susieb.l5$out_sample.addz.est, SuSiEb.MAF = susieb.maf.l5$maf.out_sample.addz.est, SuSiErss = susierss.l5$out_sample.addz.est, SuSiErss.MAF = susierss.maf.l5$maf.out_sample.addz.est)
tmp = list()
for (method in names(roc.est)) {
  TPR = roc.est[[method]]$counts$true_positive/roc.est[[method]]$counts$total_signal
  FPR = roc.est[[method]]$counts$false_positive/roc.est[[method]]$counts$total_null
  threshold = roc.est[[method]]$rates$Threshold
  tmp[[method]] = list(TPR = TPR, FPR = FPR, threshold = threshold)
}
roc.est = tmp

for (method in names(roc.est)) {
  yy = make_smooth(roc.est[[method]]$FPR, roc.est[[method]]$TPR)
  if (i == 1) {
    plot(yy$x, yy$y, t="l", col=colors[i], ylab = "True Positive Rate", xlab ="False Positive Rate", main = 'OUT addz ROC', bty='l', lwd = 3, xlim = c(0,0.004), ylim = c(0,0.4))
  } else {
    lines(yy$x, yy$y, col=colors[i], lwd = 2, xlim = c(0,0.004), ylim = c(0,0.4))
  }
  #add_text(dat[[method]]$rates$Threshold, yy$x, yy$y, 0.9, colors[i])
  add_text(roc.est[[method]]$threshold, yy$x, yy$y, 0.95, colors[i], delta = -0.0001)
  labels[i] = method
  i = i + 1
}
# legend("bottomright", legend=labels, col=colors[1:i], lty=rep(1, i), cex=0.8, lwd=rep(3, i))
```
