---
title: "SuSiE z Gaussian Benchmark"
author: "Yuxin Zou"
date: "1/16/2019"
output: workflowr::wflow_html
---

## Simulation under null

```{r}
dscout_null = readRDS('output/dscout_gaussian_null.rds')
dscout_null = dscout_null[!is.na(dscout_null$sim_gaussian_null.output.file),]
dscout_null = dscout_null[!is.na(dscout_null$susie_z.output.file),]
```

The maximum number of iteration is `r max(as.numeric(dscout_null$susie_z.niter))`. All models converge. There is no false discovry.

## Simulation with signals

```{r}
dscout_gaussian_z = readRDS('output/dscout_gaussian_z.rds')
dscout_gaussian_z = dscout_gaussian_z[!is.na(dscout_gaussian_z$sim_gaussian.output.file),]
dscout_gaussian_z = dscout_gaussian_z[!is.na(dscout_gaussian_z$susie_z.output.file),]
dscout_gaussian_z$NotConverge = dscout_gaussian_z$susie_z.niter == 100
```

L = 5, effect number = 1
```{r}
dscout_gaussian_L5 = dscout_gaussian_z[dscout_gaussian_z$susie_z.L == '5',]
dscout_gaussian_L5_E1 = dscout_gaussian_L5[dscout_gaussian_L5$sim_gaussian.effect_num == '1',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L5_E1, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 5, effect number = 2
```{r}
dscout_gaussian_L5_E2 = dscout_gaussian_L5[dscout_gaussian_L5$sim_gaussian.effect_num == '2',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L5_E2, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 5, effect number = 5
```{r}
dscout_gaussian_L5_E5 = dscout_gaussian_L5[dscout_gaussian_L5$sim_gaussian.effect_num == '5',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L5_E5, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 5, effect number = 10
```{r}
dscout_gaussian_L5_E10 = dscout_gaussian_L5[dscout_gaussian_L5$sim_gaussian.effect_num == '10',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L5_E10, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 5, effect number = 20
```{r}
dscout_gaussian_L5_E20 = dscout_gaussian_L5[dscout_gaussian_L5$sim_gaussian.effect_num == '20',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L5_E20, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 20, effect number = 1
```{r}
dscout_gaussian_L20 = dscout_gaussian_z[dscout_gaussian_z$susie_z.L == '20',]
dscout_gaussian_L20_E1 = dscout_gaussian_L20[dscout_gaussian_L20$sim_gaussian.effect_num == '1',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L20_E1, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 20, effect number = 2
```{r}
dscout_gaussian_L20_E2 = dscout_gaussian_L20[dscout_gaussian_L20$sim_gaussian.effect_num == '2',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L20_E2, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```
L = 20, effect number = 5
```{r}
dscout_gaussian_L20_E5 = dscout_gaussian_L20[dscout_gaussian_L20$sim_gaussian.effect_num == '5',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L20_E5, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

L = 20, effect number = 10
```{r}
dscout_gaussian_L20_E10 = dscout_gaussian_L20[dscout_gaussian_L20$sim_gaussian.effect_num == '10',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L20_E10, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```
L = 20, effect number = 20
```{r}
dscout_gaussian_L20_E20 = dscout_gaussian_L20[dscout_gaussian_L20$sim_gaussian.effect_num == '20',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_L20_E20, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

## Simulation initialize at true

```{r}
dscout_gaussian_init = readRDS('output/dscout_gaussian_init.rds')
dscout_gaussian_init = dscout_gaussian_init[!is.na(dscout_gaussian_init$sim_gaussian.output.file),]
dscout_gaussian_init = dscout_gaussian_init[!is.na(dscout_gaussian_init$susie_z_init.output.file),]
dscout_gaussian_init$NotConverge = dscout_gaussian_init$susie_z_init.niter == 100
```

effect number = 1
```{r}
dscout_gaussian_E1 = dscout_gaussian_init[dscout_gaussian_init$sim_gaussian.effect_num == '1',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_E1, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

effect number = 2
```{r}
dscout_gaussian_E2 = dscout_gaussian_init[dscout_gaussian_init$sim_gaussian.effect_num == '2',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_E2, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

effect number = 5
```{r}
dscout_gaussian_E5 = dscout_gaussian_init[dscout_gaussian_init$sim_gaussian.effect_num == '5',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_E5, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

effect number = 10
```{r}
dscout_gaussian_E10 = dscout_gaussian_init[dscout_gaussian_init$sim_gaussian.effect_num == '10',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_E10, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

effect number = 20
```{r}
dscout_gaussian_E20 = dscout_gaussian_init[dscout_gaussian_init$sim_gaussian.effect_num == '20',]
converge.summary = aggregate(NotConverge ~ sim_gaussian.pve, dscout_gaussian_E20, sum)
colnames(converge.summary) = c('pve', 'NotConverge')
converge.summary
```

