---
title: "SuSiE z Performance"
author: "Yuxin Zou"
date: 2019-02-24
output:
  workflowr::wflow_html:
    code_folding: hide
---

DAP-z is not stable, so we exclude it from the simulation. It has two problems:

1. The algorithm doesn't stop.

2. It uses more than 6GB memories.

There is no credible set for signals in FINEMAP. We generate the credible set of causal signals as the union of the variables included in the smallest set of causal configurations that already covered 95% of the total posterior probability.

We use datasets from `dsc-finemap`, which is from GTExV8 genotypes. The genotype matrix X is 574 by 1001.

## Simulation with signals

We simulate a gaussian y under various number of causal variables, total percentage of variance explained (PVE) and whether the signals have equal effect. The reason I control the effect size is that if we random generate the effect size for the signals, some signals have large effect size by chance. Therefore these signals have larger PVE.

We fit SuSiE with L = 5, FINEMAP with max 5 causals.

```{r eval=FALSE}
library(dscrutils)
dscout = dscquery('output/finemap_compare_small_data_signal', target='method sim_gaussian.pve sim_gaussian.n_signal sim_gaussian.effect_weight score_susie.objective score_susie.converged score.total score.valid score.size score.signal_pip score_susie.purity score_susie.top score_susie.overlap ',group = c("score: score_susie score_finemap", "method: susie_z susie_z_init finemap"))

colnames(dscout) = c('DSC', 'method', 'output.file', 'pve', 'n_signal', 'effect_weight', 'score', 'objective', 'converged', 'total', 'valid', 'size', 'signal_pip', 'purity', 'top', 'overlap')
dscout$effect_weight[which(dscout$effect_weight == 'rep(1/n_signal, n_signal)')] = 'equal'
dscout$effect_weight[which(dscout$effect_weight != 'equal')] = 'notequal'
```

```{r}
library(dplyr)
library(knitr)
library(kableExtra)
library(susieR)
dscout = readRDS('output/finemap_compare_small_data_signal_dscout_RE8.rds')
dscout.susie = dscout[dscout$method == 'susie_z',]
dscout.susie.init = dscout[dscout$method == 'susie_z_init',]
dscout.finemap = dscout[dscout$method == 'finemap',]
```

* Failed run:

There is one failed run for `susie_z`. The data has 5 signals and the total PVE is 0.8. [Problem 42](SuSiEzRProblem42.html)

* Size of CS: 

```{r}
size.susie = aggregate(size~effect_weight+n_signal+pve, dscout.susie, FUN = function(x) round(mean(x), 2))
colnames(size.susie)[colnames(size.susie) == 'size'] <- 'size.susie'
size.susie.init = aggregate(size~effect_weight+n_signal+pve, dscout.susie.init, FUN = function(x) round(mean(x), 2))
colnames(size.susie.init)[colnames(size.susie.init) == 'size'] <- 'size.susie.init'
size.finemap = aggregate(size~effect_weight+n_signal+pve, dscout.finemap, FUN = function(x) round(mean(x), 2))
colnames(size.finemap)[colnames(size.finemap) == 'size'] <- 'size.finemap'

size = Reduce(function(...) merge(...),
       list(size.susie, size.susie.init, size.finemap))
size %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Purity of CS:

```{r}
purity.susie = aggregate(purity~effect_weight+n_signal+pve, dscout.susie, FUN = function(x) round(mean(x), 3))
colnames(purity.susie)[colnames(purity.susie) == 'purity'] <- 'purity.susie'
purity.susie.init = aggregate(purity~effect_weight+n_signal+pve, dscout.susie.init, FUN = function(x) round(mean(x), 3))
colnames(purity.susie.init)[colnames(purity.susie.init) == 'purity'] <- 'purity.susie.init'

purity = Reduce(function(...) merge(...),
       list(purity.susie, purity.susie.init))
purity %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive"), full_width = F) 
```

* Power:

```{r}
valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.susie, sum)
total = aggregate(DSC~ effect_weight + n_signal + pve, dscout.susie, length)
total$total_true = total$DSC * total$n_signal
power.susie = merge(valid, total)
power.susie$power.susie = round(power.susie$valid/(power.susie$total_true), 3)
colnames(power.susie)[colnames(power.susie) == 'valid'] <- 'valid.susie'

valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.susie.init, sum)
total = aggregate(DSC~ effect_weight + n_signal + pve, dscout.susie.init, length)
total$total_true = total$DSC * total$n_signal
power.susie.init = merge(valid, total)
power.susie.init$power.susie.init = round(power.susie.init$valid/(power.susie.init$total_true), 3)
colnames(power.susie.init)[colnames(power.susie.init) == 'valid'] <- 'valid.susie.init'

valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.finemap, sum)
total = aggregate(DSC ~ effect_weight + n_signal + pve, dscout.finemap, length)
total$total_true = total$DSC * total$n_signal
power.finemap = merge(valid, total)
power.finemap$power.finemap = round(power.finemap$valid/(power.finemap$total_true),3)
colnames(power.finemap)[colnames(power.finemap) == 'valid'] <- 'valid.finemap'

power = Reduce(function(...) merge(...),
       list(power.susie, power.susie.init, power.finemap))
power = power[,-4]
power %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F) %>% add_header_above(c(" ", " ", " "," ", "SuSiE z" = 2, "SuSiE z init" = 2,"FINEMAP" = 2)) %>% column_spec(c(6, 8, 10), bold = T)
```

* FDR
```{r}
valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.susie, sum)
total = aggregate(total~ effect_weight + n_signal + pve, dscout.susie, sum)
fdr.susie = merge(valid, total)
fdr.susie$fdr.susie = round((fdr.susie$total - fdr.susie$valid)/fdr.susie$total, 3)
colnames(fdr.susie)[colnames(fdr.susie) == 'valid'] <- 'valid.susie'
fdr.susie = fdr.susie[,-5]

valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.susie.init, sum)
total = aggregate(total~ effect_weight + n_signal + pve, dscout.susie.init, sum)
fdr.susie.init = merge(valid, total)
fdr.susie.init$fdr.susie.init = round((fdr.susie.init$total - fdr.susie.init$valid)/fdr.susie.init$total, 3)
colnames(fdr.susie.init)[colnames(fdr.susie.init) == 'valid'] <- 'valid.susie.init'
fdr.susie.init = fdr.susie.init[,-5]

valid = aggregate(valid ~ effect_weight + n_signal + pve, dscout.finemap, sum)
total = aggregate(size ~ effect_weight + n_signal + pve, dscout.finemap, sum)
fdr.finemap = merge(valid, total)
fdr.finemap$fdr.finemap = round((fdr.finemap$size - fdr.finemap$valid)/fdr.finemap$size, 3)
colnames(fdr.finemap)[colnames(fdr.finemap) == 'valid'] <- 'valid.finemap'
fdr.finemap = fdr.finemap[,-5]

fdr = Reduce(function(...) merge(...),
       list(fdr.susie, fdr.susie.init, fdr.finemap))

fdr %>% kable() %>% kable_styling(bootstrap_options = c("striped", "condensed", "responsive","bordered"), full_width = F) %>% add_header_above(c(" ", " ", " ", "SuSiE z" = 2, "SuSiE z init" = 2,"FINEMAP" = 2)) %>% column_spec(c(5, 7, 9), bold = T)
```

