---
title: "SuSiE RSS NOT Converge case"
author: "Yuxin Zou"
date: "4/15/2019"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

This data is simulated with PVE 0.6. There is only one signal.

```{r}
library(susieR)
library(data.table)
r.out = as.matrix(fread('data/small_data_69.ld_out_file.out.ld'))
r.in = as.matrix(fread('data/small_data_69.ld_in_file.in.ld'))
data = readRDS('data/small_data_69_sim_gaussian_3.rds')
ss = readRDS('data/small_data_69_sim_gaussian_3_get_sumstats_1.rds')
```

```{r}
z = ss$sumstats$bhat/ss$sumstats$shat
susie_plot(z, y = "z", b=data$meta$true_coef)
```

This is the reuslt from susie_bhat:
```{r}
fit_b = susie_bhat(ss$sumstats$bhat, ss$sumstats$shat, R = r.in, n=287, L=5, estimate_residual_variance=TRUE)
susie_plot(fit_b, y='PIP', b = data$meta$true_coef)
```

susie_rss fails to converge with L = 5:
```{r}
fit_rss = susie_rss(z, R = r.in, L=5, max_iter = 20)
plot(fit_rss$elbo)
```

Using L=1, it converges.
```{r}
fit_rss_init = susie_rss(z, R=r.in, L=1)
susie_plot(fit_rss_init, y='PIP', b=data$meta$true_coef)
```

If we relax the constraint on residual variance, it converges. There is no significant credible set, and the estimated residual variance is 740.
```{r}
fit_rss_relax = susie_rss(z, R = r.in, L=5, max_iter = 20, restrict = FALSE)
```

This data is simulated with PVE 0.8. There are five signals.

```{r}
r.out = as.matrix(fread('data/small_data_132.ld_out_file.out.ld'))
r.in = as.matrix(fread('data/small_data_132.ld_in_file.in.ld'))
data = readRDS('data/small_data_132_sim_gaussian_12.rds')
ss = readRDS('data/small_data_132_sim_gaussian_12_get_sumstats_1.rds')
```

```{r}
z = ss$sumstats$bhat/ss$sumstats$shat
susie_plot(z, y = "z", b=data$meta$true_coef)
```

This is the reuslt from susie_bhat:
```{r}
fit_b = susie_bhat(ss$sumstats$bhat, ss$sumstats$shat, R = r.in, n=287, L=5, estimate_residual_variance=TRUE)
susie_plot(fit_b, y='PIP', b = data$meta$true_coef)
```

susie_rss fails to converge with L = 5. Using L=1, it converges, but it picks up the wrong one.
```{r}
fit_rss = susie_rss(z, R = r.in, L=1)
susie_plot(fit_rss, y='PIP', b = data$meta$true_coef)
```

If we relax the constraint on residual variance, it converges. There is no significant credible set, and the estimated residual variance is 9560.
```{r}
fit_rss_relax = susie_rss(z, R = r.in, L=5, max_iter = 20, restrict = FALSE)
```
